Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond to review wrt experiment details.

\subsection{Passing between two chairs}

@@

\subsection{'Put the ball on a shelf'}

>>>>

\textbf{Our whole-body motion planner generates a robot configuration
  trajectory that is sampled at a 200~Hz rate and stored in a
  file. This file can then be used to play the trajectory in open-loop
  on the HRP-2 robot, which is position-controlled. Scenarios in
  Sections \ref{sec:chairs} and \ref{sec:shelf} were both successfully
  executed.}

\subsection{Passing between two chairs}
\label{sec:chairs}

@@

\subsection{'Put the ball on a shelf'}
\label{sec:shelf}
